Modeling thermal dust emission with two components: application to the {\it PLANCK} HFI maps

### 2014-08-09 ms.tex
last pre-submission edits to introduction

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and DIRBE/\IRAS~100$\mu$m emission with a 
single-MBB spectrum. Here we investigate the FDS99 two-component dust emission 
model as an alernative parametrization for the dust spectral energy 
distribution (SED) composed  of \PLANCK~High Frequency Instrument (HFI), DIRBE 
and \IRAS~data. In doing so, we obtain maps of dust temperature and optical 
depth, both at $6.1'$ resolution. Because we employ a model that has been 
validated with FIRAS data down to submillimeter (submm) wavelengths, we expect 
our best-fit parameters to be useful in constructing high-resolution 
predictions of dust emission over a very broad range of wavelengths. This 
includes low frequencies ($<$350 GHz), which \cite{planckdust} caution their 
model may not adequately fit, and also measurements near the peak of the dust 
SED, for example \AKARI~140-160$\mu$m \citep{akari}. We also anticipate our 
derived optical depth map will serve as a valuable cross-check for extinction 
estimates based directly upon optical observations of stars 
\citep[e.g.][]{schlafly14} and as a baseline for next-generation dust 
extinction maps incorporating high-resolution, full-sky infrared data sets such
as \WISE~\citep{wright10, meisner14} and \AKARI.

>>>>

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of \PLANCK's superb, 
relatively artifact-free broadband data covering the entire sky and a wide 
range of frequencies. Towards this end, \cite{planckdust} has recently 
conducted a study modeling \PLANCK~353 GHz, 545 GHz, 857 GHz and 
DIRBE/\IRAS~100$\mu$m emission with a single-MBB spectrum. Here we investigate 
the FDS99 two-component dust emission model as an alernative parametrization 
for the 100-3000 GHz dust spectral energy distribution (SED) composed  of 
\PLANCK~High Frequency Instrument (HFI), DIRBE and \IRAS~data. In doing so, we 
obtain \PLANCK-based maps of dust temperature and optical depth, both at $6.1'$
resolution. Because we employ a model that has been validated with FIRAS down 
to millimeter wavelengths and optimized for \PLANCK, our derived parameters are
useful in constructing high-resolution predictions of dust emission over a very
broad range of wavelengths. This includes low frequencies (100-350 GHz), which 
\cite{planckdust} caution their model may not adequately fit, and also 
wavelengths near the peak of the dust SED, relevant to e.g. 
\AKARI~140-160$\mu$m \citep{akari}. We also anticipate our derived optical 
depth map will serve as a valuable cross-check for extinction estimates based 
directly upon optical observations of stars \citep[e.g.][]{schlafly14} and as a
baseline for next-generation dust extinction maps incorporating 
high-resolution, full-sky infrared data sets such as 
\WISE~\citep{wright10, meisner14} and \AKARI.
